\chapter{Relativistic quantum mechanics}

In this chapter, we will introduce the basics of the canonical quantization. We will start by introducing
Poisson brackets and its basic properties. Then we will define a quantization map $Q$ which maps the
classical dynamical variable into the operator within a Hilbert space. Using the Groenewold's theorem we
will show the map actually doesn't exist so we will end up with the naive quantization. Using this process we will then
formulate the Klein-Gordon equation, an equation for describing a spin-less particle in the quantum mechanics.
We will see that this equation is second order both in time and space which will result in some obstacles. With the
hope of solving this issue we will construct the Dirac equation which describes the $\frac{1}{2}$-spin particle.

\section{Canonical quantization}

\paragraph{} Canonical quantization is a process of transition from a classical theory to the quantum one. If a 
quantum problem has an analog in the classical mechanics we can use the process of quantization to find the formulation
in the quantum mechanics using the analogous equations in the classical one. In the classical mechanics a state of the system
is represented by coordinates in the \textit{phase space} $(\vec{q_{1}}, \dots, \vec{q_{n}}, \vec{p_{1}}, \dots, \vec{p_{n}})$.
In the quantum mechanics, the analog of $q_{i}$ and $p_{i}$ are operators $\hat{q}_{i}$ and $\hat{p}_{i}$ acting in the 
\textit{Hilbert space}.

\begin{definition}
    \label{df:poisson}
    Given two dynamical variables in the phase space $\mathcal{Q}$, \newline $f(\vec{q_{1}}, \dots, \vec{q_{n}}, \vec{p_{1}}, \dots, \vec{p_{n}}, t) 
    \in C^{\infty}(\mathcal{Q}, \mathbb{R})$ and $g(\vec{q_{1}}, \dots, \vec{q_{n}}, \vec{p_{1}}, \dots, \vec{p_{n}}, t) 
    \in C^{\infty}(\mathcal{Q}, \mathbb{R})$, the binary operation $\{f, g\}$ is called the \textbf{Poisson bracket} of these functions and takes the form

    \begin{equation}
        \{f, g\} = \sum_{i=1}^{N}\left(\partialder{f}{q_{i}} \partialder{g}{p_{i}} - \partialder{f}{p_{i}} \partialder{g}{q_{i}}\right)
    \end{equation}
\end{definition}

\begin{theorem}
    \label{th:poisson_cononical_coordinates}
    The Poisson brackets of canonical coordinates $q_{i}$ and $p_{i}$ are

    \begin{equation}
        \begin{gathered}
        \{q_{i}, q_{j}\} = 0 \\
        \{p_{i}, p_{j}\} = 0 \\
        \{q_{i}, p_{j}\} = \delta_{ij}
        \end{gathered}
    \end{equation}
\end{theorem}

\begin{proof}
    The proof of \ref{th:poisson_cononical_coordinates} can be easily done from the definition \ref{df:poisson}. 
    The first two equations are manifestly zero because $\partialder{q_{i}}{p_{j}} = \partialder{p_{i}}{q_{j}} = 0$
    and the last one can be proved as follows.

    \begin{equation}
        \begin{split}
            \{q_{i}, p_{j}\} = \sum_{k=1}^{N}\left(\partialder{q_{i}}{q_{k}} \partialder{p_{j}}{p_{k}} - \partialder{q_{i}}{p_{k}} \partialder{p_{j}}{q_{k}}\right) 
            = \sum_{k=1}^{N} \partialder{q_{i}}{q_{k}} \partialder{p_{j}}{p_{k}} = 
            \begin{cases}
                1  & \quad \text{if } i = j = k \\
                0  & \quad \text{otherwise}
            \end{cases} \\
            \implies \{q_{i}, p_{j}\} = \delta_{ij}
        \end{split}
    \end{equation}
\end{proof}

\paragraph{} Paul Dirac has formulated a principle for generating operators in $H$ from dynamical variables in $C^{\infty}(\mathcal{Q}, \mathbb{R})$. 
The famous statement goes as follows.

\begin{equation}
    \label{eq:dirac_quantization}
    \{A, B\} \to \frac{1}{i \hbar}[\hat{A}, \hat{B}]
\end{equation}

That means that if we have dynamical variables $A$ and $B$ we can get their quantum counterparts $\hat{A}$ and $\hat{B}$ and the
defining property is the equation \ref{eq:dirac_quantization}. Let's define the properties of the $Q$ map (see \cite{floarin_jung})
and then study some consequences.

\begin{definition}
    \label{df:o_map}

    Let $\mathcal{Q}$ be a position space and $H$ the corresponding Hilbert space. The quantization map is

    \begin{equation}
        Q: C^{\infty}(\mathcal{Q}, \mathbb{R}) \to Op(H) \\
    \end{equation}
    
    having the properties:

    \begin{enumerate}
        \item $Q$ is linear,
        \item $Q(f)$ is self-adjoint, $f \in C^{\infty}(\mathcal{Q}, \mathbb{R})$,
        \item the relation between commutator and the Poisson bracket is
            \begin{equation}
                \label{eq:dirac_quantization_2}
                Q(\{A, B\}) = \frac{1}{i \hbar} [\hat{A}, \hat{B}]
            \end{equation}
        \item a complete set $\{f_{1}, \dots, f_{n}\}$ is mapped to a complete set $\{Q(f_{1}), \dots, Q(f_{n})\}$,
        \item an identity $Id_{\mathcal{Q}}$ is mapped to the identity $Id_{H} = Q(Id_{\mathcal{Q}})$
    \end{enumerate}
\end{definition}

It is convenient to use $[\hat{q}_{i}, \hat{p}_{j}] = i \hbar \delta_{ij}$ and \ref{eq:dirac_quantization_2} to show
that $Q(q_{i}) = \hat{q}_{i}$. Firstly, we will rewrite $q$ using the Poisson bracket. The obvious choice is $q_{i} = \{\frac{q_{i}^{2}}{2}, p_{i}\}$.
And from the definition \ref{eq:dirac_quantization_2} we see that $Q(\{\frac{q_{i}^{2}}{2}, p_{i}\}) = \frac{1}{i \hbar}[\frac{\hat{q}_{i}^{2}}{2}, \hat{p}_{i}]$.
Using the identity for commutation relation $[AB, C] = [A, B]C + B[A, C]$ the commutator on the right-hand side can
be written as follows.\footnote{Proof by directly using the definition of 
the commutator: $[AB, C] = ABC - CAB = ABC - ACB + ACB - CAB = A [B, C] + [A, C] B$}

\begin{equation*}
    Q(x_{i}) = \frac{1}{i \hbar}\bigg[\frac{\hat{x}_{i}^{2}}{2}, \hat{p}_{i}\bigg] = 
    \frac{1}{2 i \hbar} \big(\hat{x}_{i} [\hat{x}_{i}, \hat{p}_{i}] + [\hat{x}_{i}, \hat{p}_{i}] \hat{x}_{i}\big) =
    \frac{1}{2 i \hbar} \big(\hat{x}_{i} i \hbar + i \hbar \hat{x}_{i}\big) = \hat{x}_{i}
\end{equation*}

 $Q(p) = \hat{p}$ is very similar.

\begin{equation*}
    Q(p_{i}) = \frac{1}{i \hbar}\bigg[\hat{x}_{i}, \frac{\hat{p}_{i}^{2}}{2}\bigg] = 
    \frac{1}{2 i \hbar} \big([\hat{x}_{i}, \hat{p}_{i}] \hat{p}_{i} + \hat{p}_{i} [\hat{x}_{i}, \hat{p}_{i}]\big) =
    \frac{1}{2 i \hbar} \big(i \hbar \hat{p}_{i} + \hat{p}_{i} i \hbar \big) = \hat{p}_{i}
\end{equation*}

\paragraph{Groenewold theorem} Although the procedure discussed so far might look promising it has a big problem.
If we try to find an operator corresponding to a polynomial of $q$ and $p$, $P(q, p)$, we seek a Poisson
bracket $\{P_{1}(q, p), P_{2}(q, p)\} = P(p, q)$. The problem is $P_{1}(q, p), P_{2}(q, p)$ don't
not have to be unique. Thus we may find two different expressions $\{P_{1}(q, p), P_{2}(q, p)\}$ and $\{P_{1}'(q, p), P_{2}'(q, p)\}$
for a single $P(q, p)$ and we can end up with two different commutators $[Q(P_{1}), Q(P_{2})] \neq [Q(P'_{1}), Q(P'_{2})]$.
This reasoning was done by Groenewold to proof that the quantization postulated by \ref{df:o_map} actually doesn't
exist! The proof comes in the form of a counterexample.

\begin{proof}
    Let's find a quantization of a polynomial $x^{2} p$. We can choose two different Poisson brackets, for example

    \begin{equation}
        \bigg\{\frac{x^{3}}{3}, \frac{p^{2}}{2}\bigg\} = \bigg((x^{2} p) - 0\bigg) = x^{2} p \\
    \end{equation}

    \begin{equation}
        \bigg\{x^{2} p, x p\bigg\} = \bigg((2 x p) (x) - (p) (x^{2}))\bigg) = x^{2} p \\
    \end{equation}

    Now we should find the corresponding operators.

    \begin{equation*}
        \begin{gathered}
            \bigg[\frac{\hat{x}^{3}}{3}, \frac{\hat{p}^{2}}{2}\bigg] = \frac{1}{6} \bigg(\hat{p} \big[\hat{x}^{3}, \hat{p}\big] + \big[\hat{x}^{3}, \hat{p}\big] \hat{p}\bigg) = 
            \frac{i\hbar}{2} \big(\hat{x}^{2} \hat{p} + \hat{p}\hat{x}^{2}\big)
        \end{gathered}
    \end{equation*}

    Let's use $Q (xp) = \frac{1}{2}\big(\hat{x} \hat{p} + \hat{p} \hat{x}\big)$ and the last calculation to check the result
    of the second expression.\footnote{Since $xp = \big\{\frac{x^{2}}{2}, \frac{p^{2}}{2} \big\}$, $Q(xp) = \big[\frac{x^{2}}{2}, 
    \frac{p^{2}}{2} \big] = \frac{1}{4} \big(\hat{x} [\hat{x}, \hat{p}^{2}] + [\hat{x}, \hat{p}^{2}] \hat{p}\big) = \frac{1}{2}
    (\hat{x} \hat{p} + \hat{p} \hat{x})$}

    \begin{equation*}
        \begin{gathered}
            \bigg[Q(\hat{x}^{2} \hat{p}), Q(\hat{x} \hat{p})\bigg] = \frac{1}{4} \bigg( \big[\hat{x}^{2}\hat{p}, \hat{x}\hat{p}\big] + \big[\hat{x}^{2}\hat{p}, \hat{p}\hat{x}\big] + \big[\hat{p}\hat{x}^{2}, \hat{x}\hat{p}\big] + \big[\hat{p}\hat{x}^{2}, \hat{p}\hat{x}\big] \bigg) = \\
            \frac{i \hbar}{2} \bigg(\hat{x}^{2}\hat{p} + \hat{p}\hat{x}^{2} + [\hat{x}, \hat{p}] \hat{x}\bigg) = \frac{i \hbar}{2} \bigg(\hat{x}^{2}\hat{p} + \hat{p}\hat{x}^{2}\bigg) - \hbar^{2} \hat{x}
        \end{gathered}
    \end{equation*}

    Since we got two different operators for the same starting polynomial we must conclude the quantization map doesn't exist. But
    it's not the end of the story. As is discussed in \cite{floarin_jung} we see our results differ only by $\hbar^{2}$ term. Thus
    the quantization $Q$ can be seen as a first-order approximation.

    \begin{equation}
        \label{eq:dirac_quantization}
        \{A, B\} \to \frac{1}{i \hbar}[\hat{A}, \hat{B}] + \mathcal{O}(\hbar^{2})
    \end{equation}

    Let's note, finally, that there is an extending procedure called \textit{deformation quantization} which takes into
    account all the higher powers of $\hbar$.

\end{proof}

From now, we will use the explicit form of the operators in the x-representa-\\tion. As we've seen the obstruction of
constructing the quantization map and we don't really want to deep dive into more complicated methods we will now use rather
a heuristic approach for the 1st quantization and simply use the following quantization rules for momentum and energy.

\begin{equation}
    \begin{gathered}
        p_{i} \to - i \hbar \partialder{}{x^{i}} \\
        E \to i \hbar \partialder{}{t}
    \end{gathered}
\end{equation}


\section{Klein-Gordon equation}

\paragraph{} \textit{Klein-Gordon equation} is relativistic quantum mechanical equation named after Oskar Klein and Walter Gordon and
it describes relativistic spin-less particles. It can be found using quantization of the relativistic energy equation. We need to apply the
$Q$ map on each side while taking into account that $Q(E^2) = - \hbar^{2} \partialdernd{}{t}$ and 
$Q(\vec{p}^2) = - \hbar^{2} \Delta$.

\begin{equation*}
    \begin{gathered}
        E^{2} = \vec{p}^{2} c^{2} + m^{2} c^{4} \\
        - \hbar^{2} \partialdernd{}{t} \psi = - \hbar^{2} c^{2} \Delta \psi + m^{2} c^{4} \psi
    \end{gathered}
\end{equation*}

After a little rearranging and setting $\frac{m^{2} c^{2}}{\hbar^{2}} = \mu^{2}$, we will finally get the famous form \ref{eq:klein_gordon}.

\begin{equation}
    \label{eq:klein_gordon}
    \bigg(\frac{1}{c^{2}} \partialdernd{}{t} - \Delta + \mu^{2} \bigg) \psi = 0
\end{equation}

Let's rewrite the equation in a form so we can see it is \textit{Lorentz invariant}. We use the fact that \textit{4-gradient}
transforms the same way as any other 4-vector and than express the Klein-Gordon equation using 4-gradient dot products.
Using the metric $\eta^{\mu \nu} = diag(1, -1, -1, -1)$ and the \textit{4-gradient} $\partial_{\mu} = (\partialder{}{t}, \partialder{}{x}, \partialder{}{y}, \partialder{}{z})$ 
it is possible to write the term $\frac{1}{c^{2}} \partialdernd{}{t} - \Delta$ as follows.

\begin{equation*}
     \frac{1}{c^{2}} \partialdernd{}{t} - \partialdernd{}{x} - \partialdernd{}{y} - \partialdernd{}{z} = \eta^{\mu \nu} \partial_{\mu} \partial_{\nu} = \partial_{\mu} \partial^{\mu}
\end{equation*}

\begin{equation}
    \bigg(\partial_{\mu} \partial^{\mu} + \mu^{2} \bigg) \psi = 0
\end{equation}

\section{Dirac equation}

\paragraph{} Dirac tried to find an equation that is first order in both space and time by doing the \textit{square root} 
of the Klein-Gordon equation. Let's start with the equation \ref{eq:klein_gordon}.

\begin{equation*}
    \bigg(- \frac{1}{c^{2}} \partialdernd{}{t} + \Delta - \mu^{2} \bigg) \psi = 0
\end{equation*}

We would like to find an operator $\hat{K}$ such that $\hat{K} \hat{K} = (-\frac{1}{c^{2}} \partialdernd{}{t} + \Delta - \mu^{2})$. Let's
find the $\hat{K}$ in terms of coefficients $\gamma^{0}$, $\gamma^{1}$, $\gamma^{2}$, $\gamma^{3}$. If we write $\hat{K}^{2} = (\hat{K}' + \mathbb{I} \mu)(\hat{K}' - \mathbb{I} \mu)$
we see it is sufficient to investigate the $\hat{K}'$ operator only since $(\hat{K}' + \mathbb{I} \mu)(\hat{K}' - \mathbb{I} \mu) = \big(\hat{K}'\big)^{2} - \mu^{2}$.

\begin{equation*}
    \frac{1}{c^{2}} \partialdernd{}{t} - \Delta = 
    (\gamma^{0} \frac{i}{c} \partialder{}{t} + \gamma^{1} \partialder{}{x} + \gamma^{2} \partialder{}{y} + \gamma^{3} \partialder{}{z})
    (\gamma^{0} \frac{i}{c} \partialder{}{t} + \gamma^{1} \partialder{}{x} + \gamma^{2} \partialder{}{y} + \gamma^{3} \partialder{}{z})
\end{equation*}

and by rewriting the expression above we get

\begin{equation*}
    \begin{gathered}
        (\gamma^{0} \frac{i}{c} \partialder{}{t} + \gamma^{1} \partialder{}{x} + \gamma^{2} \partialder{}{y} + \gamma^{3} \partialder{}{z})
        (\gamma^{0} \frac{i}{c} \partialder{}{t} + \gamma^{1} \partialder{}{x} + \gamma^{2} \partialder{}{y} + \gamma^{3} \partialder{}{z}) = \\
        \frac{1}{c^{2}} \partialdernd{}{t} (\gamma^{0})^{2} + \partialdernd{}{x} (\gamma^{1})^{2} + \partialdernd{}{y} (\gamma^{2})^{2} + \partialdernd{}{z} (\gamma^{3})^{2} + \\
        \partialder{}{t} \partialder{}{x} (\gamma^{0} \gamma^{1} + \gamma^{1} \gamma^{0}) + \partialder{}{t} \partialder{}{y} (\gamma^{0} \gamma^{2} + \gamma^{2} \gamma^{0}) \dots
    \end{gathered}
\end{equation*}

We see the expansion gave us the conditions for the $\gamma$'s, $(\gamma^{0})^{2} = 1$, $(\gamma^{i})^{2} = -1$ and $\gamma^{i} \gamma^{j} + \gamma^{j} \gamma^{i} = 0$
for $i \neq j \land i, j \in \{1, 2, 3\}$. To satisfy all these conditions $\gamma^{\mu}$ is clearly not a number. When Dirac was deriving the equation
he immediately recognized the gammas to be 4x4 matrices. One example of such a set of matrices is the Dirac representation.

\begin{equation*}
    \begin{gathered}
        \gamma^{0} = 
         \begin{pmatrix}
          1 & 0 & 0 & 0 \\
          0 & 1 & 0 & 0 \\
          0 & 0 & -1 & 0 \\
          0 & 0 & 0 & -1 \\
         \end{pmatrix}
        \gamma^{1} = 
         \begin{pmatrix}
          0 & 0 & 0 & 1 \\
          0 & 0 & 1 & 0 \\
          0 & -1 & 0 & 0 \\
          -1 & 0 & 0 & 0 \\
         \end{pmatrix} \\
        \gamma^{2} = 
         \begin{pmatrix}
          0 & 0 & 0 & -i \\
          0 & 0 & i & 0 \\
          0 & i & 0 & 0 \\
          -i & 0 & 0 & 0 \\
         \end{pmatrix}
        \gamma^{3} = 
         \begin{pmatrix}
          0 & 0 & 1 & 0 \\
          0 & 0 & 0 & -1 \\
          -1 & 0 & 0 & 0 \\
          0 & 1 & 0 & 0 \\
         \end{pmatrix} \\
    \end{gathered}
\end{equation*}

Let's check these matrices work correctly with all the equations $(\gamma^{0})^{2} = 1$, $(\gamma^{i})^{2} = -1$ and $\gamma^{i} \gamma^{j} + \gamma^{j} \gamma^{i} = 0$.
We can also notice that last three matrices are composed from sub-matrices having the form of Pauli matrices $\sigma^{i}$.

\begin{equation*}
    \begin{gathered}
        \sigma^{1} = 
         \begin{pmatrix}
          0 & 1 \\
          1 & 0 \\
         \end{pmatrix}, \quad
        \sigma^{2} = 
         \begin{pmatrix}
          0 & -i \\
          i & 0 \\
         \end{pmatrix}, \quad
        \sigma^{3} = 
         \begin{pmatrix}
          1 & 0 \\
          0 & -1 \\
         \end{pmatrix}
    \end{gathered}
\end{equation*}

For Pauli matrices there is the same relation we found for the gamma matrices $\sigma^{i} \sigma^{j} + \sigma^{j} \sigma^{i} = 2 
\delta_{ij} \mathbb{I}_{2 \cross 2}$. Without knowing the exact form of Pauli matrices and taking only the anti-commutation relation
we can prove the defining property holds if we rewrite the gamma matrices using a compact form with sub-matrices.

\begin{equation*}
    \begin{gathered}
        \gamma^{i} = 
        \begin{pmatrix}
             0_{2 \cross 2} & \sigma^{i} \\
              - \sigma^{i} & 0_{2 \cross 2} \\
        \end{pmatrix} \quad \implies \\
        \gamma^{i} \gamma^{j} =
        \begin{pmatrix}
             0_{2 \cross 2} & \sigma^{i} \\
              - \sigma^{i} & 0_{2 \cross 2} \\
        \end{pmatrix}
        \begin{pmatrix}
             0_{2 \cross 2} & \sigma^{j} \\
              - \sigma^{j} & 0_{2 \cross 2} \\
        \end{pmatrix} =
        - \begin{pmatrix}
             \sigma^{i} \sigma^{j} & 0_{2 \cross 2} \\
             0_{2 \cross 2} & \sigma^{i} \sigma^{j}
        \end{pmatrix} = 
    \end{gathered}
\end{equation*}

Thus we can write $\gamma^{i} \gamma^{j} + \gamma^{j} \gamma^{i} = \{\gamma^{i}, \gamma^{j}\}$ using $\{\sigma^{i}, \sigma^{j}\}$ terms.

\begin{equation*}
    \begin{gathered}
        \{\gamma^{i}, \gamma^{j}\} = - 
        \begin{pmatrix}
             \sigma^{i} \sigma^{j} & 0_{2 \cross 2} \\
             0_{2 \cross 2} & \sigma^{i} \sigma^{j}
        \end{pmatrix} - 
        \begin{pmatrix}
             \sigma^{j} \sigma^{i} & 0_{2 \cross 2} \\
             0_{2 \cross 2} & \sigma^{j} \sigma^{i}
        \end{pmatrix} = 
        - \begin{pmatrix}
            \{\sigma^{i}, \sigma^{j}\} & 0_{2 \cross 2} \\
             0_{2 \cross 2} & \{\sigma^{i},  \sigma^{j}\}
        \end{pmatrix} = - 2 \delta_{ij} \mathbb{I}_{4 \cross 4}
    \end{gathered}
\end{equation*}

The final famous form of the Dirac equation is

\begin{equation}
    \label{eq:dirac_original}
    ( i \hbar \gamma^{\mu} \partial_{\mu} + mc) \psi = 0
\end{equation}
